Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-16 Supplemental-Material-B-Annotated-Analysis.Rmd
m&r re-render fro overleaf

---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen, Department of Psychology
- ^2^Author order to be discussed; currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---

@@

@@

### ML regression

@@

\begin{equation}
(\#eq:WorkerEmptyModel)
Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
\end{equation}

@@

```{r workerModelInterceptNull}
# Create and save Model
mdlWorker$glsAttNull  <-
  gls(thermometerDutch_1 ~ 1,
      data = dtWorker$full,
      control = list(opt = "nlmimb"))

@@

\begin{equation}
(\#eq:WorkerInteractionTypeModel)
Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
\end{equation}

@@

@@

@@

@@

\begin{equation}
(\#eq:WorkerOutEmptyModel)
Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
\end{equation}

@@

@@

>>>>

---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen, Department of Psychology
- ^2^Author order to be discussed; currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

<i class="fas fa-exclamation-circle"></i> Note. All multilevel assumptions are tested as usual including (e.g., for random slopes model with _j_ within person predictors):

$$
\begin{align}
  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
  \sim \mathcal{N}
  \begin{pmatrix}
    \begin{bmatrix} 
      0 \\ 
      \vdots \\
      0
    \end{bmatrix}, 
    \begin{bmatrix} 
      \tau_{00}^2 &  & \\ 
      \vdots & \ddots & \\
      \tau_{j0} & \ldots & \tau_{jj}^2
    \end{bmatrix}
  \end{pmatrix}
\end{align}
$$

@@

### Multi-Level Regression

We then proceeded with a multilevel analysis, which also acknowledges that the measurements are nested within participants, but makes full use of the within participant variation.

@@

\begin{equation}
(\#eq:WorkerEmptyModel)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} + e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
  \end{split} 
\end{equation}

@@

```{r workerModelGls}
# Create and save Model
mdlWorker$glsAttNull  <-
  gls(thermometerDutch_1 ~ 1,
      data = dtWorker$full,
      control = list(opt = "nlmimb"))

@@

\begin{equation}
(\#eq:WorkerInteractionTypeModel)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                      &\ \beta_{1i} = \gamma_{10} \\
                      &\ \beta_{2i} = \gamma_{20}
  \end{split} 
\end{equation}

@@

mdlWorker$lmerInterceptAttTypeCI <- 
  confint(method = "Wald", mdlWorker$lmerInterceptAttType)

@@

\begin{equation}
(\#eq:WorkerRandomSlopes)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
  \end{split} 
\end{equation}

@@

# Simple (i.e., fast) CIs
mdlWorker$lmerSlopesAttTypeCI <- 
  confint(method = "Wald", mdlWorker$lmerSlopesAttType)

@@

\begin{equation}
(\#eq:WorkerOutEmptyModel)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} +  e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
  \end{split} 
\end{equation}

@@

\begin{equation}
(\#eq:workerOutInterceptAttNeedEq)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                      &\ \beta_{1i} = \gamma_{10}
  \end{split} 
\end{equation}

@@

\begin{equation}
(\#eq:workerOutSlopeAttNeedEq)
  \begin{split}
    \textrm{Level 1:} &
      \begin{aligned}[t]
        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
      \end{aligned} \\
    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
  \end{split} 
\end{equation}
